### 2020-08-21 manuscript/manuscript.rmd

---
bibliography: manuscript.bib
csl: nature.csl
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
  html_document: default
  github_document: default
---

>>>>

---
bibliography: manuscript.bib
csl: nature.csl
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
  word_document: default
  github_document: default
---
